Cell type assignments for SCPCP000015

### 2025-02-11 analyses/cell-type-ewings/exploratory_analysis/08-merged-celltypes.Rmd
remove unused template and move misplaced utils functions

```{r}
# source in setup functions prep_results()
setup_functions <- file.path(module_base, "template_notebooks", "utils", "setup-functions.R")
source(setup_functions)

@@

# source in plotting functions 
# expression_umap(), cluster_density_plot(), and annotated_exp_heatmap()
plotting_functions <- file.path(module_base, "template_notebooks", "utils", "plotting-functions.R")
source(plotting_functions)

>>>>

```{r}
# source in setup functions prep_results()
setup_functions <- file.path(module_base, "scripts", "utils", "setup-functions.R")
source(setup_functions)

@@

# source in plotting functions 
# expression_umap(), cluster_density_plot(), and annotated_exp_heatmap()
plotting_functions <- file.path(module_base, "scripts", "utils", "plotting-functions.R")
source(plotting_functions)
